caDDS: Community Assisted Distributed Database for Sequences

### 2020-07-07 Paper2020ACM/MeetingJune25.tex
Latest edits

-Intro Pg 2
✓ - 3,000,000,000 -> 3 billion
- Shorten HGP section. Combine HGP + NGS to one paragraph.
✓ - Fix typo: Genomics is is

-Intro: Database
- NGS -> high voluminous data -> need to store it in a digital format -> retrieve it for analysis

@@

Scope
- 2 things: 
- 1) create a theoretical design for a proposed system
- 2) evaluate the theoretical running time and speed of the operations.
- define here what you mean by proposed system and base system (
- base system means FTP retrieval from NCBI

>>>>

-Intro Pg 2
✓ - 3,000,000,000 -> 3 billion
✓- Shorten HGP section. Combine HGP + NGS to one paragraph.
✓ - Fix typo: Genomics is is

✓-Intro: Database
✓- NGS -> high voluminous data -> need to store it in a digital format -> retrieve it for analysis

@@

✓Scope
✓- 2 things: 
✓- 1) create a theoretical design for a proposed system
✓- 2) evaluate the theoretical running time and speed of the operations.
✓- define here what you mean by proposed system and base system (
✓- base system means FTP retrieval from NCBI

### 2020-07-07 Paper2020ACM/Paper2020.tex
Latest edits

The huge data must be stored in a form of digital information storage design as well. These are where the technologies of databases come in. Databases or (DBMS: Database Management Systems) manage the digital information, and the access to it. \cite{Silberschatz2010}. The two types of databases are the centralized and the distributed databases\cite{centralizedvsdistributed}. The centralized databases have a single node or a single access point. While distributed databases have multiple nodes, and each node contains a portion or a replica of the data. Distributed databases are more complex but have higher availability, faster response, and is better for collaborative work. For genomic research, when the data storage needs to be increased often, distributed databases are most appropriate.

@@

The project will focus on creating a framework, and outlining key API features of the framework. The current scope of the project is as follows:

\begin{itemize}
    \item To create a framework for a proposed system
    \item To design the correctness of a system
    \item To look at the basic time complexity of the base system (NCBI) and the proposed system
    \item To compare the proposed system to the base system

\end{itemize}

>>>>

The huge data must be stored in a form of digital information storage design as well. These are where the technologies of databases come in. Databases or DBMS (Database Management Systems) manage the digital information, and the access to it. \cite{Silberschatz2010}. The two types of databases are the centralized and the distributed databases\cite{centralizedvsdistributed}. The centralized databases have a single node or a single access point. While distributed databases have multiple nodes, and each node contains a portion or a replica of the data. Distributed databases are more complex but have higher availability, faster response, and are better for collaborative work. For genomic research, when the data storage needs to be increased often, distributed databases are most appropriate.

@@

The research will focus on creating a theoretical design for the proposed system. And to evaluate the theoretical properties of the proposed system and the base system. The proposed system is the caDDS (community assisted Distributed Databases for Sequences), specifically the GET operation. While the base system, is the FTP (File Transfer Protocol) of NCBI for getting sequences. NCBI is currently a complex platform, but the scope of this research will only be the FTP access route.
